\documentclass[a4paper,11pt,notitlepage]{report}
% Henrik Lund Kramshoej, February 2001
% hlk@security6.net,
% My standard packages
\usepackage{zencurity-network-exercises}

\begin{document}

\rm
\selectlanguage{english}

\newcommand{\course}[1]{KEA System Integration 2020\\ exercises}

\mytitle{KEA System Integration 2020}{hand-in assignment I}

\pagenumbering{roman}


\setcounter{tocdepth}{0}

\normal



\chapter*{Hand-in assignment I: Describe the system environment for an organisation}

{\bf Assignment:}\\
Consider a system environment running the services we have presented in this course. The services are:

\begin{list2}
\item Tomcat J2EE server, we ran this early in the course and this can be used for running Camel in production
\item Camel we have run this multiple times during the course
\item PostgreSQL Server
\end{list2}

Create a report describing the following in main chapters:

\begin{list2}
\item Company back story, create back story similar to the SOA book chapter 2 for your fictive company
\item Describe the software requirements for each of the above systems and create summary of the environment as a whole. Any synergies?\\
Dont forget that these systems cannot float in free space, but requires one or more operating systems, which you must choose. Maybe include some monitoring and configuration management like Ansible.
\item Describe the hardware requirements for your initial deployment, taking into account creating a more production ready system. Do you need development, staging, testing, production systems, some redundancy?
\item Suggest an initial deployment overview - little detail, with a naming scheme to use for servers, physical and virtual
\item Create a list of skills requirements for running this environment. Consider job postings for similar jobs, and you may copy parts of that and adapt
\end{list2}

Note: you decide the versions to base this on.

The report should include the following sections at least:
\begin{list2}
\item Title, Table of contents, formal report thanks
\item Confidentiality agreement -- Write "Confidential" on each page
\item Executive summary -- big companies always want this
\item Information about the scan done, what was it
\item Scope and targets
\item Review of all targets -- detailed information and recommendations
\item Conclusion -- may be more technical
\item Appendices -- various information, Whois info about subnets and prefixes
\end{list2}


Must be handed in as PDF and latest on May 1, 2020. Teams up to three are allowed. Make sure to list team members in the report.

Expect PDF as A4, portrait mode around 10 pages with illustrations as needed. No more than 15 pages.

Recommend to use a report template with table of contents, front matter, page numbers etc. You can use Word, Google Docs, LaTeX, whatever you feel most comfortable with.


Help:\\
Think about what you would like to receive if you were responsible for buying hardware, selecting software and hiring people.

Notes: The above reference to the SOA book, is the book:\\
\emph{Service-Oriented Architecture: Analysis and Design for Services and Microservices},\\ Thomas Erl, 2017
ISBN: 978-0-13-385858-7

\end{document}
