\documentclass[a4paper,11pt,notitlepage]{report}
% Henrik Kramselund Jereminsen, February 2001
% hlk@security6.net,
% My standard packages
\usepackage{zencurity-network-exercises}

\begin{document}

Uploaded to fronter friday march 20, 13:18

Dear all,

During this time we will not be meeting face to face at Lygten, as announced by KEA. We will though try to follow the plan as usual:
https://zencurity.gitbook.io/kea-it-sikkerhed/system-integration/lektionsplan

and I have added more exercises than usual. So coming monday and next week I would like for you to do these things:
Read the chapters, as previously announced chapters 1-5 in the SOA book. note: There are a lot of figures in the chapters.

Download the newly uploaded/updated documents in the ressource folder here:
system-integration-exercises.pdf
6-SOA-EAI-ESB-system-integration.pdf
hand-in-assigments-kea-integration.pdf

Do the 5 exercises listed in the file 6-SOA-EAI-ESB-system-integration.pdf: Run PostgreSQL, Why go to SOA, Cloud Computing Introduction, Cloud Deployment
Download the Microservices ebook . I hope this provides flexibility and is possible in your current situation, kids, work, life etc.

I will announce Zoom meetings starting monday morning at 9, hoping you can find the time to join in and say hi. I will not be doing live teaching at this time, but you will be able to ask questions and get help for the exercises.

They will start monday
Topic: Test meeting
Time: Mar 23, 2020 09:00 AM Copenhagen
        Every day, until Mar 29, 2020, 7 occurrence(s)
        Mar 23, 2020 09:00 AM
        Mar 24, 2020 09:00 AM
        Mar 25, 2020 09:00 AM
        Mar 26, 2020 09:00 AM
        Mar 27, 2020 09:00 AM
        Mar 28, 2020 09:00 AM
        Mar 29, 2020 09:00 AM
Please download and import the following iCalendar (.ics) files to your calendar system.
Daily: https://zoom.us/meeting/tJQsdeuqrj0q_xNRoe15ul4tHW6ogph-7g/ics?icsToken=98tyKuCorzkoGNSTsF39Y7UtE5n8bPGxk05WhJFSmU6wFiwHdivBYO1FIroyR9-B

Join Zoom Meeting
https://zoom.us/j/901222060

Meeting ID: 901 222 060

We will also start a hand-in assignment which allow group work. This is described in the hand-in document referenced above.

all for now, stay safe, wash your hands!
