\documentclass[a4paper,11pt,notitlepage,landscape]{report}
% Henrik Kramselund Jereminsen, February 2001
% hlk@security6.net,
% My standard packages
\usepackage{zencurity-one-page}
%\usepackage{lscape}

\begin{document}

\rm
\selectlanguage{english}

\newcommand{\subject}[1]{SIEM and Log Analysis course}

%\mytitle{SIEM and Log Analysis}{exercises}
%{\LARGE Kickstart: SIEM and Log Analysis}{}
\lhead{\fancyplain{}{\color{titlecolor}\bfseries\LARGE Kickstart: SIEM and Log Analysis}}


\normal

This material is prepared for use in \emph{\subject} and was prepared by
Henrik Kramselund Jereminsen, \url{xhek@kea.dk} \url{hkj@zencurity.dk}.
It contains the very basic information to get started!

These course and exercises are expected to be performed in a training setting with network connected systems. The exercises use a number of tools which can be copied and reused after training. A lot is described about setting up your workstation in the Github repositories.

{\bf The main site is: \link{https://github.com/kramse/}} I try to gather all information there!\\
So to get kickstarted in this course:

\begin{list1}
\item[\faSquareO] Make sure you can login to Fronter \link{https://kea-fronter.itslearning.com/}\\
Electronic version of this document will be uploaded here!
\item[\faSquareO] Bookmark the main Github page: \link{https://github.com/kramse/}\\
Note: there are two pinned repositories \verb+security-courses+ and \verb+kramse-labs+
\item[\faSquareO] Lecture plan for this course is in Fronter\\
(Source is also in Git \link{https://github.com/kramse/kea-it-sikkerhed}
\item[\faSquareO] Slides and exercises booklet -- clone or download single files\\
\link{https://github.com/kramse/security-courses/tree/master/courses/system-and-software/siem-log-analysis}
\item[\faSquareO] Check BIOS settings - make sure CPU settings have virtualisation turned ON
\item[\faSquareO] Select and install virtualisation software -- you choose the software
\item[\faSquareO] Read about setup of exercise systems here\\
\link{https://github.com/kramse/kramse-labs}\\
We need the Debian 12 for this course only, but if you can give it at least 8Gb of memory 
\item[\faSquareO] Get the books! Either on paper or PDF\\
You can do a trial on O'Reilly online and get access for a limited time, if you dont have the books available.
\end{list1}

I hope we will have a fun and enjoyable time in this course.


\end{document}
