\documentclass[a4paper,11pt,notitlepage]{report}
% Henrik Kramselund Jereminsen, February 2001
% hlk@security6.net,
% My standard packages
\usepackage{zencurity-network-exercises}

\begin{document}

\rm
\selectlanguage{english}

\newcommand{\emne}[1]{Software Security course}
\newcommand{\kursus}[1]{Software Security course}
\newcommand{\kursusnavn}[1]{Software Security course\\ exercises}

\mytitle{Software Security}{hand-in assignments}

\pagenumbering{roman}


\setcounter{tocdepth}{0}

\normal



\chapter*{Hand-in 1: Django newsletter signup application}

{\bf Assignment:}\\
Create a basic Application using the Django project framework.

The application should include a form for signup to a newsletter, and save this information.
The fields to accept are: Username,First names, Last names, Email

A script for adding test data to this system should also be developed - make sure it contains some bad data too.

Must be handed in as PDF and code at latest on October 10, 2021. Teams up to three are allowed. Make sure to list team members in the report.

You are expected to use no more than 20-30 hours on this. Main takeaway is to understand frameworks such as Django exist, not to make a secure production ready application.
If you run out of time during the project, describe how far you got - and importantly what obstacles you met.

Code must be handed in as zip or link to repository, if private Github repository used should allow access to Github user \verb+kramse+

Help:\\
Using the Django admin site can help by showing data entered in your application. You dont need to program much more than a single form and possibly a front page or menu.


The report should include the following sections at least:
\begin{list2}
\item Title, Table of contents, formal report thanks
\item Confidentiality agreement -- Write "Confidential" on each page
\item Appendices
\end{list2}

Expect PDF as A4, portrait mode up to 5-10 pages with illustrations as needed. Maximum 15 pages.

Recommend to use a report template with table of contents, front matter, page numbers etc. You can use Word, Google Docs, LaTeX, whatever you feel most comfortable with.

{\bf We will do the hand-in through Fronter!}


\end{document}
\chapter*{Hand-in 2: Django input validation}


{\bf Assignment:}\\
Extend your basic Application using the Django project framework to use input validation.

The application for newsletter signup has had some problems with data quality and possibly exploits.

To alleviate this you must extend your application and environment:
\begin{list2}
\item Implement input validation in your application so any future data entered is validated before being saved
\item Create a method, script or program to evaluate existing data
\item Write a procedure for data conversion/check and perform this as a \emph{production change} on your system - with documentation how the change was performed. Include this in the report as an appendix.
\end{list2}

Must be handed in as one PDF and one code zip or repository at latest on October 8st, 2019. Teams up to two are allowed. Make sure to list team members in the report.

Expect PDF as A4, portrait mode up to 5-10 pages with illustrations as needed.
Recommend to use a report template with table of contents, front matter, page numbers etc.

Code must be handed in as zip or link to repository, if private Github repository used should allow access to user \verb+kramse+


\end{document}
