\documentclass[a4paper,11pt,notitlepage,landscape]{report}
% Henrik Kramselund Jereminsen, February 2001
% hlk@security6.net,
% My standard packages
\usepackage{zencurity-one-page}
%\usepackage{lscape}

\begin{document}

%\rm
\selectlanguage{english}

\lhead{\fancyplain{}{\color{titlecolor}\bfseries\LARGE Hand-in assignment I: KEA System Security F2022 course}}

\normal


{\bf Assignment:}\\
Consider a system environment for an organisation running the basic services. The services are:

\begin{list2}
\item Time service
\item Network service -- at least a single device routing, firewalling and switching
\item Domain Name Service (DNS) -- both autoritative and resolvers? you decide
\end{list2}

Create a report describing the following in main chapters:

\begin{list2}
\item Company back story, create back story for your fictive company, half a page
\item Describe the software requirements for each of the above systems, copy paste the requirements from a home page for some software perhaps\\
Dont forget that these systems cannot float in free space, but requires one or more operating systems. Maybe include some monitoring and configuration management like Ansible.
\item Describe the hardware requirements for your initial proof-of-concept deployment or what is there now.
Evaluate if this is sufficient for a more production ready system. Do you need some redundancy or scalability?
\item Suggest an initial deployment overview or document what is there now -- include a little detail, with a naming scheme to use for servers, physical and virtual\\
I would probably end up with about 10 devices for a small PoC
\item Create a list of skills requirements for running this environment. Consider job postings for similar jobs, and you may copy parts of that and adapt
\end{list2}

Note: you decide the versions to base this on.

The report should include the following sections at least:
\begin{list2}
\item Title
\item Confidentiality agreement -- Write "Confidential" on each page
\item Overview - description of the project
\item Table of contents, page numbers, headlines - business report style
\item Results - including method description and screenshots
\item Executive summary
\item Appendices
\end{list2}


{\bf Formal requirements:}\\
To be handed in at latest February 21, 2022 by fronter, or email to xhek@kea.dk

Teams up to 3 are allowed. Make sure to list team members in the report.

Expect PDF as A4, portrait mode around 15 pages with illustrations as needed.
No more than 25 pages if 3 members.

Recommend to use a report template with table of contents, front matter, page numbers etc. You can use Word, Google Docs, \LaTeX, whatever you feel most comfortable with.

You are NOT expected to spend more than 25-30 hours on this. Less is also OK.

The report is not graded, but feedback will be given.

{\bf Hints:}\\
Consider this a proposal for your imaginary management team.

Help may be found in the Defensive Security Handbook, about Asset Management and Documentation

Hints about running these services can be found in the documents \emph{Campus Network Security: High Level Overview} and \emph{Campus Operations Best Current Practice}, both are from the Network Startup Resource Center.

Think about what you would like to receive if you were responsible for buying hardware, selecting software and hiring people.

If you need more help contact me,\\


Henrik Kramselund, \url{xhek@kea.dk}

\end{document}
