\documentclass[a4paper,11pt,notitlepage]{report}
% Henrik Kramselund Jereminsen, February 2001
% hlk@security6.net,
% My standard packages
\usepackage{zencurity-network-exercises}

\begin{document}

\rm
\selectlanguage{english}

\newcommand{\course}[1]{KEA Kompetence Penetration Testing\\ exercises}

\mytitle{KEA Kompetence Communication and Network Security}{hand-in assignments}

\pagenumbering{roman}


\setcounter{tocdepth}{0}

\normal

\chapter*{Hand-in 1: Dump a HTTP connection with password}

{\bf Assignment:}\\
Find a device that provides a web administration interface over HTTP - not HTTPS.

Preferably one with a simple username and password admin/admin.

Capture a HTTP session, hint: using tcpdump or wireshark might be the easiest.

Create a report about how the password is sent, in clear text, or perhaps as base 64 and why this is insecure.

Include screenshot.

Create a report, inspiration for report template below.

I suggest the report should include the following sections at least:
\begin{list2}
\item Title, Table of contents, formal report template thanks
\item Executive summary -- big companies always want this
\item Information about the network dump done, what was it
\item Review of password security when running HTTP
\item Argue why HTTPS would be better, and if you like show similar dump with HTTPS
\item Conclusion -- may be more technical
\item Appendices -- various information, Whois info about subnets and prefixes
\end{list2}

You are very much welcome to run multiple tools!

Must be handed in as PDF by Fronter and latest on May 19, 2022 23:59 . Teams up to two are allowed. Make sure to list team members in the report.

Expect PDF as A4, portrait mode up to 5-10 pages with illustrations as needed. Double if team.

Expected time usage, 10-20 hours at most.

Help:\\
Think about what you would like to receive if you were management about to approve a security policy disallowing HTTP based logins.


\end{document}
