\documentclass[a4paper,11pt,notitlepage,landscape]{report}
% Henrik Kramselund, February 2001
% hlk@zencurity.com,
% My standard packages
\usepackage{zencurity-one-page}
%\usepackage{lscape}

\begin{document}

\rm
\selectlanguage{english}

\newcommand{\subject}[1]{Communication \& Network Security}

\lhead{\fancyplain{}{\color{titlecolor}\bfseries\LARGE Skills Exercise: \subject}}

\normal

This material is prepared for use in \emph{\subject} and was prepared by
Henrik Kramselund, \url{xhek@kea.dk}.


These course and exercises are expected to be performed in a training setting with network connected systems, but what are the pre-requisites?!

As we go through the exercises today, try to focus on pre-requisites and skills needed.


\begin{list2}
\item[\faSquareO] What are some technical skills needed?
\vskip 5mm
\item[\faSquareO] Do you need knowledge of specific platforms? (operating systems, application platforms)
\vskip 5mm
\item[\faSquareO] Do you need knowledge and skills about specific work flows?
% Like git clone, git commit, git push
\vskip 5mm
\item[\faSquareO] Is programming a requirement? is scripting? -- what is the difference?
\end{list2}

Security wise we also have presented a lot of terms, concepts, systems, which ones help with security?
\begin{list2}
\item[\faSquareO] Does basic skills in an area help you secure it? (loaded question I think)
\vskip 5mm
\item[\faSquareO] How do we ensure that we know enough within each area?
\vskip 5mm
\item[\faSquareO] Which are the most important areas within information security?
\vskip 5mm
\item[\faSquareO] Which areas require specialist skills?
\vskip 5mm
\item[\faSquareO] Do you need to know about cloud to work in information security?
\end{list2}


{\bf\LARGE\color{red}Do NOT look at the next pages yet!}

\eject



{\bf Baseline Skills}

\begin{list2}\small
\item Threat-Centric Security, NSM, and the NSM Cycle
\item TCP/IP Protocols
\item Common Application Layer Protocols
\item Packet Analysis
\item Windows Architecture
\item Linux Architecture
\item Basic Data Parsing (BASH, Grep, SED, AWK, etc)
\item IDS Usage (Snort, Suricata, etc.)
\item Indicators of Compromise and IDS Signature Tuning
\item Open Source Intelligence Gathering
\item Basic Analytic Diagnostic Methods
\item Basic Malware Analysis
\end{list2}

Source: \emph{Applied Network Security Monitoring Collection, Detection, and Analysis}, Chris Sanders and Jason Smith

\eject
{\bf Security engineering a job role}

On any given day, you may be challenged to:
\begin{list2}\small
\item Create new ways to solve existing production security issues
\item Configure and install firewalls and intrusion detection systems
\item Perform vulnerability testing, risk analyses and security assessments
\item Develop automation scripts to handle and track incidents
\item Investigate intrusion incidents, conduct forensic investigations and incident responses
\item Collaborate with colleagues on authentication, authorization and encryption solutions
\item Evaluate new technologies and processes that enhance security capabilities
\item Test security solutions using industry standard analysis criteria
\item Deliver technical reports and formal papers on test findings
\item Respond to information security issues during each stage of a projects lifecycle
\item Supervise changes in software, hardware, facilities, telecommunications and user needs
\item Define, implement and maintain corporate security policies
\item Analyze and advise on new security technologies and program conformance
\item Recommend modifications in legal, technical and regulatory areas that affect IT security
\end{list2}

Source: \url{https://www.cyberdegrees.org/jobs/security-engineer/}\\
also
\url{https://en.wikipedia.org/wiki/Security_engineering}


\end{document}
