\documentclass[a4paper,11pt,notitlepage,landscape]{report}
% Henrik Kramselund Jereminsen, February 2001
% hlk@security6.net,
% My standard packages
\usepackage{zencurity-one-page}
\usepackage{tabularx}

\begin{document}

\rm
\selectlanguage{danish}

\newcommand{\subject}[1]{Intro to Incident Response - Track B}

%\mytitle{SIEM and Log Analysis}{exercises}
%{\LARGE Kickstart: SIEM and Log Analysis}{}
\lhead{\fancyplain{}{\color{titlecolor}\bfseries\LARGE Exerciser: \subject}}


\normal

Welcome to your new role as CISO -- Chief Information Security Officer, and incident response.

Since we don't have an actual company we will use your current life and use of IT systems for these exercises.

I will reference the CIS controls (version 7.1). We don't need the full framework, but if you want to check it out after it is available at: \link{https://www.cisecurity.org/controls}

You can use these papers for notes.


\eject
\section*{Exercise 1 - max 15 min}

{\bf CIS Control 1: Inventory and Control of Hardware Assets}

Organisations should have an overview of which hardware assets they use. Who uses them, where they are, what type it is, what is their service contracts etc.

Make a short list of your groups  \emph{hardware}

\begin{list1}
\item[\faSquareO] Which phone types do you have, high level Apple, Android, others?
\item[\faSquareO] Which brands of laptops do you have?
\item[\faSquareO] Which other similar hardware do you have? Tablets etc.
\end{list1}

Discuss if you think this sounds important, or registering this is a waste of time.


{\bf CIS Control 2: Inventory and Control of Software Assets}

Like hardware organisations use a lot of money on software. Which kinds of software is your group dependent on in your day to day lives -- include a few portals like Facebook, Instagram, Tik tok, Snapchat

\begin{list1}
\item[\faSquareO] Which operating systems do you use: Windows, Mac, Linux, Chromebook, others?
\item[\faSquareO] Most critical applications: text processing?
\item[\faSquareO] Email programs?
\item[\faSquareO] Which browsers do you use?
\end{list1}

We know all software has errors and bugs! So we need to update these continously, but how does an organisation get an overview -- using this control.

\eject

\section*{Exercise 2 - max 15 min}

{\bf CIS Control 3: Continuous Vulnerability Management}
\begin{list1}
\item[\faSquareO] When was your devices last updated?
\item[\faSquareO] Have you ever been hit by a virus or ransomware?
\item[\faSquareO] How often should you update your computers and applications?
\end{list1}

Discuss among yourselves, have you turned on auto-update? Why / Why not?


\eject

\section*{Exercise 3 - max 15 min}


{\bf CIS Control 10: Data Recovery Capabilities}

\begin{list1}
\item[\faSquareO] What is a backup of data?
\item[\faSquareO] Have you ever lost data, maybe a hand-in for studies or digital pictures?
\item[\faSquareO] How often should one backup data?
\item[\faSquareO] Is it needed to keep multiple generations of data?
\end{list1}

Discuss what is the easiest way to do backup, learn from each other.


\eject

\section*{Incident Log }


\begin{tabularx}{\textwidth-1cm}{|p{3cm}|X|} \hline
Time & Description \\\hline
& \\\hline
& \\\hline
& \\\hline
& \\\hline
& \\\hline
& \\\hline
\end{tabularx}


\section*{Financial }

\begin{tabularx}{\textwidth-1cm}{|p{3cm}|X|p{3cm}|} \hline
Time & Description & Cost \\\hline
& & \\\hline
& & \\\hline
& & \\\hline
& & \\\hline
& & \\\hline
& & \\\hline
& & \\\hline
& & \\\hline
& & \\\hline
& & \\\hline
& & \\\hline
& & \\\hline
& & \\\hline
& & \\\hline
& & \\\hline
{\bf Total} & & \\\hline
\end{tabularx}

\eject

\section*{Incident }

An incident happened!

We will now roll the dice!

D6 is a 6-sided dice, D12 is 12-sides.

Calculate with this table what incident it is, what it will cost your company.

\begin{tabularx}{\textwidth-1cm}{|p{4cm}|X|p{7cm}|p{3cm}|} \hline
{\bf Initial Access D6} & {\bf Access Level D12} & {\bf Cleanup Cost D6} & {\bf Time line D12} \\\hline
1 Phishing   & 1 Initial Access & Simple 10.000 DKK & 1 month\\\hline
2 Vira/worms & 2 Execution & Actual incident 50.000 DKK &2 months\\\hline
3 Known CVE  & 3 Persistence & Medium 250.000 DKK & 3 months\\\hline
4 Known CVE  & 4 Priv esc & Large 500.000 DKK &4 months\\\hline
5 0-day      & 5 Defense Evasion & X-Large 1.000.000 DKK & 5 months\\\hline
6 Unknown    & 6 Credential Access & Super Large 10.000.000 DKK & 6 months\\\hline
             & 7 Discovery & & 7 months \\\hline
             & 8 Lateral Movement & & 8 months \\\hline
             & 9 Collection & & 9 months \\\hline
             & 10 Command and Control & & 10 months\\\hline
             & 11 Exfiltration & & 11 months\\\hline
             & 12 Impact & & 12 months \\\hline
{\bf Total} & & \\\hline
\end{tabularx}

Mitre ATT\&CK \link{https://attack.mitre.org/} -- column Initial Access is considered 1 in this game.



\end{document}
